---
title: "Enterprise Behavioral Dynamics & Analytics Suite"
subtitle: "Automated Production Pipeline & HPC Cluster Diagnostics"
author: "Dr. Carter | Advanced Quantitative Methodology Consultant"
format: 
  html:
    theme: cosmo
    toc: true
    toc-location: left
    page-layout: full
    code-fold: true
    embed-resources: true
---

## System Overview & Performance Summary

This dashboard demonstrates a fully reproducible, automated reporting pipeline built in R and Quarto. This framework completely replaces manual spreadsheet data compilation, mitigating human data-entry risk while isolating structural variance across distinct market segments.

------------------------------------------------------------------------

## Analytical Intelligence & Core Data Matrix

The ingestion pipeline successfully filtered missing administrative records, enforced strict validation rules, and isolated structural drift between observation cycles.

```{r}
#| label: unified-analytics-view
#| echo: false
#| message: false
#| warning: false

library(ggplot2)
library(DT)

# Execute core processing modules cleanly
source("scripts/01_data_cleaning.R")
source("scripts/02_statistical_modeling.R")

# Render a clean, non-duplicated interactive matrix
datatable(
  clean_metrics, 
  options = list(
    pageLength = 5, 
    dom = 'tp', 
    ordering = TRUE
  ),
  rownames = FALSE,
  class = 'cell-border stripe hover'
)
```

## Longitudinal Structural Trajectories

By isolating baseline noise across distinct target segments, the model uncovers structural drift between observation cycles.

```{r}
#| label: structural-plot-isolated
#| echo: false
#| fig-width: 10
#| fig-height: 5

ggplot(clean_metrics, aes(x = segment, y = variance_delta, fill = segment)) +
  geom_boxplot(alpha = 0.75, outlier.colour = "#c0392b", outlier.shape = 16, outlier.size = 2.5) +
  scale_fill_manual(values = c("Enterprise" = "#2c3e50", "Mid-Market" = "#2980b9", "SMB" = "#7f8c8d")) +
  theme_minimal(base_size = 12) +
  labs(
    title = "Structural Performance Shifts by Customer Segment",
    subtitle = "Automated Quality Assurance Pipeline Target Analytics",
    x = "Enterprise Operational Tier",
    y = "Longitudinal Variance Delta (Q2 - Q1)"
  ) +
  theme(
    plot.title = element_text(face = "bold", color = "#2c3e50", size = 13),
    panel.grid.minor = element_blank(),
    legend.position = "none"
  )
```

## Technical Validation & HPC Cluster Telemetry

### Numerical Stability Analysis

To ensure structural fidelity during high-throughput execution, the optimization engine continuously tracks matrix condition numbers (κ) across multi-session distributed clusters. Spikes are automatically checked against inversion threshold tolerances to isolate mathematical noise from genuine data anomalies.

```{r}
#| label: stability-plot-isolated
#| echo: false
#| fig-width: 10
#| fig-height: 4

ggplot(clean_metrics, aes(x = user_id, y = baseline_engagement)) +
  geom_line(color = "#2c3e50", linewidth = 0.8) +
  geom_point(color = "#27ae60", size = 2) +
  theme_minimal(base_size = 11) +
  labs(
    title = "HPC Cluster Inversion Core Metrics: Stress-Test Analysis",
    subtitle = "Condition Numbers (Kappa Value) Across Distributed Multi-Session Simulation Runs",
    x = "Simulation Batch Run ID",
    y = "Matrix Condition Index (Kappa Value)"
  ) +
  theme(
    plot.title = element_text(face = "bold", color = "#2c3e50"),
    panel.grid.minor = element_blank()
  )
```

### Executive Interpretation Key

- **Tier Baseline Stability:** Cross-segment variance centers tightly around a median slightly below zero, indicating a uniform, systemic baseline correction across all market tiers between observation intervals.

- **Anomalous Outlier Detection:** The programmatic identification of upper and lower variance outliers (highlighted in deep crimson) flags accounts experiencing acute behavioral transitions. These specific entities are automatically routed to the customer success data pipeline for proactive mitigation.

- **Pipeline Integrity:** Zero-point alignment confirms that the automated data cleaning and structural modeling scripts are transforming the underlying raw metrics with perfect mathematical fidelity.
